How to Name a Real-World Object, and how not

### 2019-12-06 papers/ACL2020/manynames.tex
add commented out verification interface figure back; Carina why u remove?
tweaks mainly to section 3.2

We conducted a second round of annotation where we asked people whether each name for a given image was adequate and, if not, what type of inadequacy it was.
Moreover, we asked them to indicate which names were likely intended for the same real-world object.
The task interface is shown in figure~\ref{fig:verification-interface} in the appendix.
Adequacy was rated on a 3-point scale from ``perfectly adequate'' to ``there may be a (slight) inadequacy'' to ``totally inadequate'', represented by appropriate rage faces.
We provided (and clarified by means of explanation and visual examples) the following definition: \textit{a name is ``adequate'' if there is an object in the image, whose visible parts are tightly circumscribed by the red bounding box, that one could reasonably call by that name}.
When the participant selected slightly or totally inadequate, four additional icons would appear to indicate the type of inadequacy: ``linguistic mistake'', ``named object not tightly in bounding box'', ``named object mistaken for something it's not'', and ``something else''.
We provided detailed instructions and examples at the top, as well as informative hover texts on all the buttons.

Because the quality of the data we gather in this phase will be essential for gaining insight into our data from phase one, as well as for evaluating computational object naming models (section~\ref{sec:experiments}), we set up a rigorous quality control protocol.
Every task included between 10\% and 20\% automatically generated quality control items of various kinds (names for objects in a different image, names for other objects in the same image, WordNet synonyms of given names, inserted typos, and more).
Participants would get a warning if, upon submitting their results, their accuracy on these items was below 90\%, and the advice to not do any more tasks of this type if it was below 80\%.
After every round we blocked annotators with low (<90\%) average accuracy, removed their results from the dataset and republished the relevant tasks to ensure consistent coverage of our data.

We implemented our task on Amazon Mechanical Turk (\url{https://mturk.com}).
We relied on 255 mostly recurring workers, who did a total of 9491 published tasks.
Each task would present the worker with 6 or 7 images, for a total of between 20 and 30 names.
We offered a reward of \$0.50 with an additional bonus of \$0.15 if all control items were answered correctly as extra incentive (which happened about half the time).
Our approach was valued by the workers for the interesting task, natural interface and good reward.

\mw{Maybe the following should go in 3.3 analysis? I think it fits here though.}
We reached high inter-annotator agreement: adequacy judgments (encoded on a scale from 0 to 2) have a standard deviation of 0.19, with the proportion of annotators agreeing on ``adequate'' being 88\%; the proportion of annotators agreeing on inadequacy type (the 4 options) is 86\%, and this agreement is 94\% on the judgments of whether two names were intended for the same object.
Bearing in mind that the latter often required our participants to do some kind of mind-reading -- which object could someone who entered an inadequate name plausibly have in mind? -- this level is agreement is very high.

\mw{Probably the following should go to 3.3 analysis}
For our analysis below we aggregate our judgments of adequacy by taking the mean, and judgments of inadequacy type by taking the majority (also counting ``none'' if there was no inadequacy).
As for the judgments of whether two names were intended for the same object, we use two different types of aggregations, for different purposes.
For evaluating computational object naming models, we want to know primarily whether a name generated by a model could have been intended to name the same object as the entry-level name (i.e., the most frequent name).
This we compute by a simple majority rule: true if name1 and name2 were judged to be for the same object by a majority of annotators, and false otherwise.
However, we are also interested in more general statistics, e.g., the mean number of names per object, and the relative frequencies of names for a given object.
For this, we need to compute clusters of names  (the pairwise majority rule does not result in a proper clustering): as distance between names we use the proportion of annotators saying they do not name the same object, and we perform agglomerative, complete-linkage clustering with a threshold of .5 (i.e., all pairs of names in a cluster must name the same object according to a majority of annotators).
A disadvantage of this (hard) clustering method is that every name can only be in one cluster, i.e., name only one object. \mw{But this is not as bad as it sounds! It's often quite plausible, e.g., that food names the pizza, not the topping!}
This way, our method may slightly underestimate the number of names per object.
(The alternative -- soft clustering, where each name could potentially be in multiple clusters -- risks overestimating the number of named objects in an image.)

@@

\paragraph{Of Verification Annotations}
\cs{@gbt @mw}

>>>>

We conducted a second round of annotation where we asked people whether each name for a given image was adequate and, if not, what type of inadequacy it was.
Moreover, we asked them to indicate which names were likely intended for the same real-world object.
The task interface is shown in figure~\ref{fig:verification-interface} in the appendix.
Adequacy was rated on a 3-point scale from ``perfectly adequate'' to ``there may be a (slight) inadequacy'' to ``totally inadequate'', represented by appropriate emotes.
We provided (and clarified by means of explanation and visual examples) the following definition: \textit{a name is ``adequate'' if there is an object in the image, whose visible parts are tightly circumscribed by the red bounding box, that one could reasonably call by that name}.
When the participant selected slightly or totally inadequate, four additional icons would appear to indicate the type of inadequacy: ``linguistic mistake'', ``named object not tightly in bounding box'', ``named object mistaken for something it's not'', and ``something else''.
We provided detailed instructions and examples at the top, as well as informative hover texts on all the buttons.

Because the quality of the data we gather in this phase will be essential for gaining insight into the ManyNames dataset, as well as for evaluating computational models (section~\ref{sec:experiments}), we conducted rigorous quality control.
Every task included around 15\% automatically generated quality control items of various kinds (names for objects in a different image, names for other objects in the same image, WordNet synonyms of given names, inserted typos, and more).
When trying to submit their results, participants would get a warning if their accuracy on these items was below 90\%, and the advice to stop doing these tasks if it was below 80\%, with the option to double-check their responses.
They would get a bonus of \$0.15 if all control items were answered correctly (happened about half the time).
After every round we blocked annotators with low ($<$90\%) average accuracy, removed their results from the dataset and republished the relevant tasks to ensure consistent coverage of our data.

We implemented this verification task on Amazon Mechanical Turk (\url{https://mturk.com}). 
Basic numbers and results are reported in Table~\ref{tab:verification-numbers}.
\begin{table}[t]
	\centering
	\small
	\begin{tabular}{|ll|ll|}
		\hline
		\multicolumn{2}{|c|}{\textbf{Task setup:}} & \multicolumn{2}{c|}{\textbf{Results:}} \\ \hline
		Images: & 19427 &
			Annotators: & 255 \\
		Img-name pairs: & 69356 &
			Annotators/task: & $\geq$ 3 \\
		Tasks: & 3052 &
			Adeq. mean: & \hspace{-3em}.80 (std .093)\\
		Images/task: & 6-7 &			
			Agreement (adeq.) & 88\% \\ 
		Names/task: & 20-30 &
			Agr. (inadeq. type): & 86\% \\
		\multicolumn{2}{|l|}{Task reward: \ \$.50 (+.15)} & 
			Agr. (same-obj): & 94\% \\
		\hline
	\end{tabular}
	\caption{Verification task overview.}
	\label{tab:verification-numbers}
\end{table}
Average name adequacy, encoded on a scale $[0,1]$, is 0.80 with small standard deviation (0.093). 
Inter-annotator agreement is high also by other measures: the proportion of annotators agreeing on ``adequate'' is 88\%, agreeing on inadequacy type is 86\%, and agreeing on whether two names were intended for the same object is 94\%.
This level is agreement is high given the complexity of the task (e.g., pictures sometimes unclear), especially bearing in mind that we essentially asked our participants to do some kind of mind-reading (i.e., which object could someone who entered an inadequate name plausibly have had in mind?).
Figure~\ref{fig:verification-piechart} shows the proportion of `adequate' judgments and the types of inadequacies our annotators reported.
\begin{figure}[t]
	\centering
	\hspace*{.2\columnwidth}\includegraphics[width=.7\columnwidth]{images/verification_piechart.pdf}
	\caption{Verification results (counting individual annotations). Lighter shade within a hue indicates slight/possible error of that type; darker shade severe error.}
	\label{fig:verification-piechart}
\end{figure}

% We relied on 255 mostly recurring workers, who did a total of 9491 published tasks.
% Each task would present the worker with 6 or 7 images, for a total of between 20 and 30 names.
% We offered a reward of \$0.50 with an additional bonus of \$0.15 if all control items were % answered correctly as extra incentive (which happened about half the time).
% Our approach was valued by the workers for the interesting task, natural interface and good reward.

@@

\paragraph{Of Verification Annotations}

We aggregate our name adequacy judgments (representing adequate as 1, slightly inadequate as 0.5 and totally inadequate as 0) by taking the mean, and inadequacy type judgments by taking the majority (also counting ``none'' if there was no inadequacy).
As for the judgments of whether two names were intended for the same object, we use two different types of aggregations, for different purposes.
For evaluating computational object naming models, we want to know primarily whether a name generated by a model could have been intended to name the same object as the entry-level name (i.e., the most frequent name).
This we compute by a simple majority rule: true if name1 and name2 were judged to be for the same object by a majority of annotators, and false otherwise.
However, we are also interested in more general statistics, e.g., the mean number of names per object, and the relative frequencies of names for a given object.
For this, we need to compute clusters of names  (the pairwise majority rule does not result in a proper clustering): as distance between names we use the proportion of annotators saying they do not name the same object, and we perform agglomerative, complete-linkage clustering with a threshold of .5 (i.e., all pairs of names in a cluster must name the same object according to a majority of annotators).
A disadvantage of this (hard) clustering method is that every name can only be in one cluster, i.e., name only one object. \mw{But this is not as bad as it sounds! It's often quite plausible, e.g., that food names the pizza, not the topping!}
This way, our method may slightly underestimate the number of names per object.
The alternative -- soft clustering, where each name could potentially be in multiple clusters -- would risk overestimating the number of names per object, as well as the number of named objects in an image.

\cs{@gbt @mw}
